Crowdsourced geometric morphometrics enable rapid large-scale collection and

### 2015-04-22 manuscript/manuscript.Rmd
Update MS with new plots

---
title: Crowdsourced geometric morphometrics enable rapid large-scale collection and
  analysis of phenotypic data
author:
- affiliation: ucla
  email: jonathan.chang\@ucla.edu
  footnote: Author for correspondence jonathan.chang\@ucla.edu
  name: Jonathan Chang
- affiliation: ucla
  name: Michael E. Alfaro
bibliography:
- library.bib
- knitcitations.bib
output:
  pdf_document:
    fig_caption: yes
    keep_tex: yes
    latex_engine: xelatex
    template: inc/mstemplate.tex
  html_document:
    toc: yes
  word_document: default
documentclass: inc/msarticle
fontsize: 11pt
geometry: margin=1.2in
layout: preprint
lineno: yes
linestretch: 1.05
csl: inc/methods-in-ecology-and-evolution.csl
running_head: Fast crowdsourced phenotypic data collection
address:
- address: |
    Department of Ecology and Evolutionary Biology, University of California, Los Angeles, CA, USA
  code: ucla
word_count: 5000?
---

@@

```{r sum_table}
no_st <- fish_landmarks %>% filter(role != "student") %>% mutate(role = factor(role))

@@

meds <- pcaed %>% group_by(family, role, mark) %>% summarise(med=median(PC1)) %>% ungroup() %>% spread(role, med) %>% transmute(family, mark, value = log(abs(turker - morphologist)), stat="median")

@@

all_stats <- bind_rows(meds, mads) %>% spread(stat, value)
```

```{r geomorph_lm, eval=FALSE, cache=TRUE}
fmted <- format_for_gpagen(no_st)
allsplit <- str_split_fixed(dimnames(fmted)$id, "_", 3)
family_vec <- allsplit[, 1]
role_vec <- allsplit[, 2]
ind_vec <- allsplit[, 3]
gpaed <- gpagen(fmted, ShowPlot=F)

@@

```{r median_tbl, echo=F, results="asis", anchor="table", fig.cap="Median table"}
med_wide <- meds %>% spread(key=family, value=value)
med_wide %>% knitr::kable(digits = 2, caption = "Median table")
```

```{r mad_tbl, echo=F, results="asis", anchor="table", fig.cap="MAD table"}
mad_wide <- mads %>% spread(key=family, value=value)
mad_wide %>% knitr::kable(digits = 2, caption="MAD table")
```

```{r turker_v_expert, anchor="figure"} 
ggplot(all_stats, aes(median, mad, label=mark)) + geom_text() + labs(x="Accuracy", y="Precision")
```

@@

CV_sum <- left_join(CV_sum, CV_sum2)

# format for display
CV_sum %>% transmute(`Family`=family, `LDA`=error, `QDA`=qda_error) %>% knitr::kable(digits=3, caption="Misprediction rate of linear discriminant analysis (LDA) and quadratic discriminant analysis (QDA) with 10-fold cross validation for each fish image.")
```

@@

```{r turk_morph_procrustes_space, echo=FALSE, fig.cap="Hello", fig.keep="last", anchor="figure", message=FALSE}

@@

```{r timing_plot, echo=FALSE, fig.cap="Line plot showing time to receive results for any given image (x axis) and the total fraction of the data set received (y axis). Landmarks were first received 6 minutes after creation of the Amazon MTurk task, and at least one replicate was received for every image at the 80 minute mark."}
# median time (in minutes) it takes an expert to measure these fishes
timings <- (no_st %>% group_by(role) %>% summarise(duration=median(duration))) %>% mutate(total_time=duration * nrow(res2))

@@

# data collection time plot
fish_families %>% group_by(worker, tip) %>% summarise(time=min(time_taken)) %>% arrange(time) %>% mutate(seq = 1:n(), frac = seq / n()) %>% ggplot(aes(dseconds(time) / eminutes(), frac)) + geom_line() + labs(x="Time taken (in minutes) to receive data for one unique replicate", y="Fraction of image set complete") + theme_minimal() + xlim(0, NA)

>>>>

---
title: Crowdsourced geometric morphometrics enable rapid large-scale collection and
  analysis of phenotypic data
author:
- affiliation: ucla
  email: jonathan.chang\@ucla.edu
  footnote: Author for correspondence jonathan.chang\@ucla.edu
  name: Jonathan Chang
- affiliation: ucla
  name: Michael E. Alfaro
bibliography:
- library.bib
- knitcitations.bib
output:
  pdf_document:
    fig_caption: yes
    keep_tex: yes
    latex_engine: xelatex
    template: inc/mstemplate.tex
  html_document:
    toc: yes
  word_document: default
documentclass: inc/msarticle
fontsize: 11pt
geometry: margin=1.2in
layout: preprint
lineno: yes
linestretch: 1.05
csl: inc/methods-in-ecology-and-evolution.csl
running_head: Fast crowdsourced phenotypic data collection
address:
- address: |
    Department of Ecology and Evolutionary Biology, University of California, Los Angeles, CA, USA
  code: ucla
word_count: 6000?
---

@@

```{r sum_table, echo=FALSE}
no_st <- fish_landmarks %>% filter(role != "student") %>% mutate(role = factor(role))

@@

meds <- pcaed %>% group_by(family, role, mark) %>%
  summarise(med=median(PC1)) %>%
  ungroup() %>%
  spread(role, med) %>%
  transmute(family, mark, value = (abs(turker - morphologist)), stat="median")

@@

all_stats <- bind_rows(meds, mads) %>% spread(stat, value) %>% group_by(family) %>% mutate(lowerq=quantile(median)[2], upperq=quantile(median)[4], iqr=IQR(median), outlier = median > iqr * 2 + upperq) %>% select(-lowerq, -upperq, -iqr)

full_family <- data_frame(
  family=c("Aca", "Apo", "Bal", "Cha", "Gob", "Lab", "Pom", "Sco", "Tet"),
  full_family=c("Acanthuridae", "Apogonidae", "Balistidae", "Chaetodontidae", "Gobiidae", "Labridae", "Pomacentridae", "Scorpaenidae", "Tetraodontidae")
)

all_stats %<>% left_join(full_family) %>% mutate(outlier_label = ifelse(outlier, as.character(mark), NA))
```

```{r turker_v_expert, fig.cap="Test figure caption", anchor="figure"}
ggplot(all_stats, aes(median, mad, color=outlier)) + geom_point() + labs(x="Accuracy", y="Precision") + facet_wrap(~full_family) + geom_dl(aes(label=outlier_label), size=1, list("top.bumptwice", dl.trans(y=y+0.1), cex=0.75)) + scale_color_manual(values=c("black", "red")) + ylim(-max(abs(all_stats$mad) + 0.25), max(abs(all_stats$mad) + 0.25)) + theme("legend.position" = "none")
```

```{r geomorph_lm, eval=FALSE, echo=FALSE, cache=TRUE}
fmted <- format_for_gpagen(no_st)
allsplit <- str_split_fixed(dimnames(fmted)$id, "_", 3)
family_vec <- allsplit[, 1]
role_vec <- allsplit[, 2]
ind_vec <- allsplit[, 3]
gpaed <- gpagen(fmted, ShowPlot=F)

@@

```{r median_tbl, eval=F, echo=F, results="asis", anchor="table", fig.cap="Median table"}
med_wide <- meds %>% spread(key=family, value=value)
med_wide %>% knitr::kable(digits = 2, caption = "Median table")
```

```{r mad_tbl, eval=F, echo=F, results="asis", anchor="table", fig.cap="MAD table"}
mad_wide <- mads %>% spread(key=family, value=value)
mad_wide %>% knitr::kable(digits = 2, caption="MAD table")
```

@@

CV_sum <- left_join(CV_sum, CV_sum2) %>% left_join(full_family, by="family")

# format for display
CV_sum %>% transmute(`Family`=full_family, `LDA`=error, `QDA`=qda_error) %>% knitr::kable(digits=3, caption="Misprediction rate of linear discriminant analysis (LDA) and quadratic discriminant analysis (QDA) with 10-fold cross validation for each fish image.")
```

@@

```{r, echo=FALSE}

@@

```{r timing_plot, echo=FALSE, fig.cap="Line plot showing time to receive results for any given image (x axis) and the total fraction of the data set received (y axis). Landmarks were first received `r timing_data[[1, 'time']] %>% dminutes()` after creation of the Amazon MTurk task, and at least one replicate was received for every image at the 80 minute mark."}
# median time (in minutes) it takes an expert to measure these fishes
timings <- (no_st %>% group_by(role) %>% summarise(duration=median(duration))) %>% mutate(total_time=duration * nrow(res2))

@@

# data collection time plot
timing_data <- fish_families %>% ungroup() %>% group_by(tip) %>% summarise(time=min(time_taken)) %>% arrange(time) %>% mutate(frac=1:n()/n())

ggplot(timing_data, aes(time, frac)) + geom_line() + labs(x="Time taken (in minutes) to receive data for one unique replicate", y="Fraction of image set complete") + theme_minimal() + xlim(0, NA)
